---
title: "Shefali-group2data"
output: html_document
date: "2023-03-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#packages
```{r}
#install.packages("ggplot2")
```

#Load Libraries 
```{r}
library(tidyverse)
library(janitor)
library(naniar)
library(RColorBrewer)
library(ggplot2)
```

#Load Data and Clean Names
```{r}
sharktank <- read_csv("data/Shark Tank US dataset.csv") %>%
  clean_names()

names(sharktank)
```

#Create New Data Frame That Cleans the Data 
```{r}

##updated in office hours
sharktank_long <- sharktank %>% 
  rename(original_offer_investment_equity = original_offered_equity) %>% 
  relocate(contains("_investment_equity")) %>% 
  relocate(contains("_investment_amount")) %>% 
  pivot_longer(barbara_corcoran_investment_amount : guest_investment_equity,
      names_to = c("shark", "investment_type"),
    names_sep = "_investment_",
    values_to = "dollars") %>% 
  relocate(shark, investment_type, dollars)

sharktank_long

```


#Updated Data Frame Above to Filter the Products That Got No Investments 
```{r}
##updated in office hours
sharktank_long_invested <- sharktank %>% 
  rename(original_offer_investment_equity = original_offered_equity) %>% 
  relocate(contains("_investment_equity")) %>% 
  relocate(contains("_investment_amount")) %>%
  filter(!is.na(barbara_corcoran_investment_equity) |
         !is.na(mark_cuban_investment_equity)       |
         !is.na(lori_greiner_investment_equity)     |
         !is.na(robert_herjavec_investment_equity)  |
         !is.na(daymond_john_investment_equity)     |
         !is.na(kevin_o_leary_investment_equity)    |
         !is.na(guest_investment_equity) 
         ) %>% 
  pivot_longer(barbara_corcoran_investment_amount : guest_investment_equity,
    names_to = c("shark", "investment_type"),
    names_sep = "_investment_",
    values_to = "dollars") %>% 
  relocate(shark, investment_type, dollars)

sharktank_long_invested
```


#Types of Industries Included in the Data Set 
```{r}
table(sharktank$industry)
```

#Making Bar Graphs that Compare the Original Equity Amount to the Amount the Sharks Actually Got 

##(FOOD AND BEVERAGE) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Food and Beverage") %>% 
  arrange(desc(total_deal_equity))
```

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Food and Beverage") %>%
  filter(startup_name == "WineBalloon"|
           startup_name == "NutsnMore"|
           startup_name == "Maven'sCreamery"|
           startup_name == "Chapul"|
           startup_name == "WickedGoodCupCakes")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Shark", title = "Children/Education Equity")+
  coord_flip()
```

#Checking That Bar Graphs Only Include The Companies That Got Investments 
```{r}
sharktank %>%
  filter(industry == "Food and Beverage") %>% 
  filter(got_deal == "1")
```


##(FASHION/BEAUTY) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Fashion/Beauty") %>% 
  arrange(desc(total_deal_equity))
```

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Fashion/Beauty") %>%
  filter(startup_name == "Evrewares"|
           startup_name == "Ta-TaTowels"|
           startup_name == "PiperWei"|
           startup_name == "RuckPackCombatNutrition"|
           startup_name == "MakeupJunkieBags")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Shark", title = "Children/Education Equity")+
  coord_flip()
```

##(LIFESTYLE/HOME) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Lifestyle/Home") %>% 
  arrange(desc(total_deal_equity))
```

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Lifestyle/Home") %>%
  filter(startup_name == "CoolWraps"|
           startup_name == "Biaggi"|
           startup_name == "MCSquares"|
           startup_name == "DrainWig"|
           startup_name == "Blueland")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Shark", title = "Lifestyle/Home Equity")+
  coord_flip()
```




##OTHER GRAPHS - NOT INCLUDED

##(AUTOMOTIVE) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Automotive") %>% 
  arrange(desc(total_deal_equity))
```

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Automotive") %>%
  filter(startup_name == "MokiDoorstep"|
           startup_name == "PickupPools"|
           startup_name == "DropStop"|
           startup_name == "TheSmartWheel"|
           startup_name == "WaiveCar")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Shark", title = "Automotive Industry Equity")+
  coord_flip()
```

##(BUSINESS SERVICES) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Business Services") %>% 
  arrange(desc(total_deal_equity))
```

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Business Services") %>%
  filter(startup_name == "TotalMerchantResources"|
           startup_name == "PastabyHudson"|
           startup_name == "VerbalizeItApp"|
           startup_name == "Sapre"|
           startup_name == "HireSanta")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Shark", title = "Business Services Equity")+
  coord_flip()
```

##(CHILDREN/EDUCATION) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Children/Education") %>% 
  arrange(desc(total_deal_equity))
```

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Children/Education") %>%
  filter(startup_name == "ClassroomJams"|
           startup_name == "TheCoolWazoo"|
           startup_name == "DreamlandBaby"|
           startup_name == "TheCoop"|
           startup_name == "Jack'sStands&Marketplaces")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Shark", title = "Children/Education Equity")+
  coord_flip()
```

##(FITNESS/SPORTS/OUTDOORS) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Fitness/Sports/Outdoors") %>% 
  arrange(desc(total_deal_equity))
```

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Fitness/Sports/Outdoors") %>%
  filter(startup_name == "TheUROClub"|
           startup_name == "LineCutterz"|
           startup_name == "Radiate"|
           startup_name == "UnderTheWeather"|
           startup_name == "BollyX")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Shark", title = "Children/Education Equity")+
  coord_flip()
```

##(GREEN/CLEAN TECH) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Green/CleanTech") %>% 
  arrange(desc(total_deal_equity))
```

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Green/CleanTech") %>%
  filter(startup_name == "PittMoss"|
           startup_name == "Nohbo"|
           startup_name == "SwayMotorsports"|
           startup_name == "BetterLifeCleaningProducts"|
           startup_name == "Stasher")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Shark", title = "Children/Education Equity")+
  coord_flip()
```

##(HEALTH/WELLNESS) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Health/Wellness") %>% 
  arrange(desc(total_deal_equity))
```

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Health/Wellness") %>%
  filter(startup_name == "AvaTheElephant"|
           startup_name == "Breathometer"|
           startup_name == "Manscaped"|
           startup_name == "BugBiteThing"|
           startup_name == "EZCPak")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Shark", title = "Children/Education Equity")+
  coord_flip()
```


