---
title: "Sharktank - Rafael"
output: html_document
date: "2023-03-07"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(janitor)
library(naniar)
library(RColorBrewer)
library(ggthemes)
library(paletteer)
library(ggplot2)
library(ggrepel)
```

Load data in

```{r}
sharktank <-readr::read_csv("data/Shark Tank US dataset.csv") %>% slice_head(n = 991)
#slice to remove season 12 data
```

Take a look

```{r}
glimpse(sharktank)
```

clean the names

```{r}
sharktank <- clean_names(sharktank)
names(sharktank)
```

Separate the `business_description` column

```{r}
sharktank <- sharktank %>% 
  separate(business_description, into= c("business_name", "business_description"), sep = " - ")
#gives error because some businesses do not have a description
```

Removing dashes from ends of business names

```{r}
sharktank$business_name <- gsub("-$", "", sharktank$business_name)
```

Look at NA's

```{r}
miss_var_summary(sharktank)
```


# Looking at trends across seasons

How many products each season?

```{r}
sharktank %>% 
  count("season_number")
```

How many episodes each season?

```{r}
sharktank %>% 
  group_by(season_number) %>% 
  summarize(episode_count = n_distinct(episode_number))

#We will not include season 12 in the comparison since there is only 1 episode in the data set
```

### Find the most popular type of product for each season and make it a bar graph

How many types of industries are there, and what are they?
```{r}
sharktank %>% 
  tabyl(industry) %>% 
  arrange(desc(n))
```

Graph for all seasons
```{r}
my_palette <- paletteer_d("ggthemes::Tableau_20")

sharktank %>% 
  ggplot(aes(x=industry, fill = industry)) +
  geom_bar(alpha = 0.8)+
  theme(axis.text.x = element_text(angle = 70, hjust = 1), axis.text = element_text(size = 8)) +
  labs(title = "Industry Frequency for All Seasons",
       x = "Industry",
       y = "Occurences",
       fill = "Industry")+
 scale_fill_manual(values=my_palette)

```

```{r}
sharktank_industry <- sharktank %>% 
  group_by(industry) %>% 
  summarize(occurences = n()) 


sharktank_industry2 <- sharktank_industry %>% 
  mutate(csum = rev(cumsum(rev(occurences))), 
         pos = occurences/2 + lead(csum, 1),
         pos = if_else(is.na(pos), occurences/2, pos))

 ggplot(sharktank_industry, aes(x = "" , y = occurences, fill = fct_inorder(industry))) +
  geom_col(width = 1, color = 1) +
  coord_polar(theta = "y") +
  scale_fill_manual(values=my_palette) +
  geom_label_repel(data = sharktank_industry2,
                   aes(y = pos, label = paste0(occurences)),
                   size = 4.5, nudge_x = 1, show.legend = F) +
  guides(fill = guide_legend(title = "Industry")) +
  theme_void()+
  labs(title = "Industry Frequency for All Seasons",
       )
```



```{r}
png(filename="shark_piechart.png", width = 300, height = 300, res=300, bg = "transparent")

ggplot(sharktank_industry, aes(x = "" , y = occurences, fill = fct_inorder(industry))) +
  geom_col(width = 1, color = 1) +
  coord_polar(theta = "y") +
  scale_fill_manual(values=my_palette) +
  geom_label_repel(data = sharktank_industry2,
                   aes(y = pos, label = paste0(occurences)),
                   size = 4.5, nudge_x = 1, show.legend = FALSE) +
  guides(fill = guide_legend(title = "Industry")) +
  theme_void()+
  labs(title = "Industry Frequency for All Seasons",
       )
dev.off()
```


look at this stat for a single season season
```{r}
sharktank %>% 
  filter(season_number == "5") %>% 
  tabyl(industry) %>% 
  arrange(desc(n))
```

Facet wrap to see this stat for each season

```{r}
sharktank %>% 
  ggplot(aes(x=industry, fill = industry)) +
  geom_bar(alpha = 0.8)+
  facet_wrap(~season_number)+
   theme(axis.text.x = element_text(angle = 70, hjust = 1), axis.text = element_text(size = 5)) +
  labs(title = "Industry fequency per season",
       x = "Industry",
       y = "Occurences",
       fill = "Industry")+
   scale_fill_manual(values=my_palette)
```

### Find the most invested in industries for each season (by doing invested #/not invested #)

Proportion of each industry that is invested in
```{r}
sharktank %>% 
  filter(season_number == "5") %>% 
  group_by(industry) %>% 
  summarize(proportion_invested_in = sum(got_deal)/n()) %>% 
  arrange(desc(proportion_invested_in))
```


Remove industry if there are less than 5 pitches
```{r}
sharktank %>% 
  filter(season_number == "5") %>% 
  group_by(industry) %>% 
  filter(n()>5) %>% 
   tabyl(industry) %>% 
  arrange(desc(n))
```


Proportion of each industry that is invested in (removed the industry if there are less than 5 pitches for that industry)
```{r}
(proportion <- sharktank %>% 
  filter(season_number == "5") %>% 
  group_by(industry) %>% 
  filter(n()>5) %>% 
  summarize(proportion_invested_in = sum(got_deal)/n()) %>% 
  arrange(desc(proportion_invested_in)))
```

plot the proportion of each industry that is invested in (for a single season)
```{r}
proportion %>% 
  ggplot(aes(x= industry, y= proportion_invested_in, fill = industry)) + 
    geom_col(alpha = 0.8)+
   theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   scale_fill_manual(values=my_palette)+
   labs(title = "Industry Frequency for All Seasons",
       x = "Industry",
       y = "Proportion Invested In",
       fill = "Industry")
```
Now show proportion for all seasons
```{r}
sharktank %>% 
  group_by(industry) %>% 
  filter(n()>5) %>% 
  summarize(proportion_invested_in = sum(got_deal)/n()) %>% 
  arrange(desc(proportion_invested_in)) %>% 
    theme_gray()+
    geom_col(alpha = 0.8)+
   theme(axis.text.x = element_text(angle = 60, hjust = 1))+
   scale_fill_manual(values=my_palette)+
   labs(title = "Proportion of Industry Pitches that Earned Investments",
       x = "Industry",
       y = "Proportion Invested In",
       fill = "Industry")
 
```
## Number of investments per shark per season

Change data frame to have sharks and their investment count
```{r}
sharktank <- sharktank%>% 
pivot_longer(barbara_corcoran_investment_amount : guest_investment_equity,
      names_to = c("shark", "investment_type"),
    names_sep = "_investment_",
    values_to = "dollars") %>% 
  relocate(shark, investment_type, dollars)%>% 
  filter(investment_type != "equity")


sharktank["dollars"][is.na(sharktank["dollars"])] <- 0
   
sharktank <- sharktank %>% mutate(made_deal=ifelse(dollars>0, 1, 0))

sharktank$shark <- gsub("_", " ", sharktank$shark)
sharktank$shark <- str_to_title(sharktank$shark)
sharktank
  
```


```{r}

png(filename="C:/Users/rafae/OneDrive/Desktop/BIS15W2023_Group2/RMD Files/shark_investments.png", width = 1000, height = 1200, res=1000, bg = "transparent")
sharktank %>% 
  group_by(season_number, shark) %>% 
  summarize(number_investments = sum(made_deal)) %>% 
  ggplot(aes(x=shark, y= number_investments, fill = shark))+ geom_col()+
  scale_fill_manual(values=my_palette)+
   theme(axis.text.x = element_text(angle = 60, hjust = 1))+
    labs(title = "Number of Investments by Each Shark",
       x = "Shark",
       y = "Number of Investments",
       fill = "Shark")
ggsave("shark_investments2.png")
dev.off()
```


Shark changes in each season
