---
title: "Shefali-group2data"
output: html_document
date: "2023-03-02"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#packages
```{r}
#install.packages("ggplot2")
#install.packages("paletteer")
```

#Load Libraries 
```{r}
library(tidyverse)
library(janitor)
library(naniar)
library(RColorBrewer)
library(ggplot2)
library(paletteer)
```

#Load Data and Clean Names
```{r}
sharktank <- read_csv("data/Shark Tank US dataset.csv") %>%
  clean_names()

names(sharktank)
```

#Create New Data Frame That Cleans the Data 
```{r}

##updated in office hours
sharktank_long <- sharktank %>% 
  rename(original_offer_investment_equity = original_offered_equity) %>% #renamed title so that is was more similar to other titles in dataset 
  #used relocate feature to move column positions to make it easier to find
  relocate(contains("_investment_equity")) %>% 
  relocate(contains("_investment_amount")) %>% 
  #used pivot longer to make the shark and investment_type columns - made it easier to graph and compare equity values 
  pivot_longer(barbara_corcoran_investment_amount : guest_investment_equity,
      names_to = c("shark", "investment_type"),
    names_sep = "_investment_",
    values_to = "dollars") %>% 
  relocate(shark, investment_type, dollars)

sharktank_long

```


#Updated Data Frame Above to Filter the Products That Got No Investments 
```{r}
##updated in office hours
sharktank_long_invested <- sharktank %>% 
  rename(original_offer_investment_equity = original_offered_equity) %>% 
  relocate(contains("_investment_equity")) %>% 
  relocate(contains("_investment_amount")) %>%
  #filter to only have products that go investments  
  filter(!is.na(barbara_corcoran_investment_equity) |
         !is.na(mark_cuban_investment_equity)       |
         !is.na(lori_greiner_investment_equity)     |
         !is.na(robert_herjavec_investment_equity)  |
         !is.na(daymond_john_investment_equity)     |
         !is.na(kevin_o_leary_investment_equity)    |
         !is.na(guest_investment_equity) 
         ) %>% 
  pivot_longer(barbara_corcoran_investment_amount : guest_investment_equity,
    names_to = c("shark", "investment_type"),
    names_sep = "_investment_",
    values_to = "dollars") %>% 
  relocate(shark, investment_type, dollars)

sharktank_long_invested
```

#Clean the Names to Remove the "_"
```{r}
sharktank_long_invested$shark <- gsub("_", " ", sharktank_long_invested$shark)
sharktank_long_invested$shark <- str_to_title(sharktank_long_invested$shark)

sharktank_long_invested
```


#Types of Industries Included in the Data Set 
```{r}
table(sharktank$industry)
```

#Making Bar Graphs that Compare the Original Equity Amount to the Amount the Sharks Actually Got 



#Choosing a Color Palette
```{r}
my_palette <- paletteer_d("ggthemes::Tableau_20")
```



##(FOOD AND BEVERAGE) Bar Graphs

```{r}
#Finding the average equities for each industry 
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Food and Beverage") %>%
  filter(shark == "Mark Cuban") %>%
  filter(!is.na (total_deal_equity)) %>% 
  arrange(desc(total_deal_equity))
```

```{r}
#Creating bar graphs for the average equities
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Food and Beverage") %>%
  filter(shark == "Mark Cuban"| shark == "Original Offer") %>% 
  filter(startup_name == "WineBalloon"|
           startup_name == "NutsnMore"|
           startup_name == "ReelyHookedFishCo."|
           startup_name == "Avocaderia"|
           startup_name == "Snacklins")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Offer", title = "Food and Beverage Equity")+
  coord_flip()+
  scale_fill_manual(values=my_palette)
```

#Checking That Bar Graphs Only Include The Companies That Got Investments 
```{r}
sharktank %>%
  filter(industry == "Food and Beverage") %>% 
  filter(got_deal == "1")
```


##(FASHION/BEAUTY) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Fashion/Beauty") %>%
  filter(shark == "Daymond John") %>%
  filter(!is.na (total_deal_equity)) %>% 
  arrange(desc(total_deal_equity))
```


```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Fashion/Beauty") %>%
  filter(shark == "Daymond John"| shark == "Original Offer") %>% 
  filter(startup_name == "Nubrella"|
           startup_name == "WurkinStiffs"|
           startup_name == "CombatFlipFlops"|
           startup_name == "SunStaches"|
           startup_name == "PurseCase")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Offer", title = "Fashion/Beauty Equity")+
  coord_flip()+
  scale_fill_manual(values=my_palette)
```

##(LIFESTYLE/HOME) Bar Graphs

```{r}
sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Lifestyle/Home") %>%
  filter(shark == "Lori Greiner") %>%
  filter(!is.na (total_deal_equity)) %>% 
  arrange(desc(total_deal_equity))
```

```{r}
 sharktank_long_invested %>% 
  filter(investment_type == "equity") %>% 
  filter(industry == "Lifestyle/Home") %>%
  filter(shark == "Lori Greiner"| shark == "Original Offer") %>% 
  filter(startup_name == "ScreenMend"|
           startup_name == "MonkeyMat"|
           startup_name == "ScrubDaddy"|
           startup_name == "Urbio"|
           startup_name == "Outer")%>% 
  ggplot(aes(x = shark, y = dollars, fill = shark))+
  geom_col(position = "dodge")+
  facet_wrap(~startup_name)+
  labs(y = "Percent Equity", x = "Offer", title = "Lifestyle/Home Equity")+
  coord_flip()+
  scale_fill_manual(values=my_palette)
```

